Analysis Stand Features 

### 2018-01-24 analysis/analysis_stand_features.Rmd
update distance-dependet indices

compe_summary <- compe %>%  
  mutate(ba_ha = (ba * 10000)/(pi*100)) %>% 
  group_by(site) %>% 
  dplyr::select(ba_ha, std, site) %>% 
  dplyr::summarise(ba_mean = mean(ba_ha), 
                   ba_sd = sd(ba_ha),
                   stand_density_mean = mean(std), 
                   stand_density_sd = sd(std)) %>% 
  as.data.frame()

>>>>

compe_summary <- compe %>%  
  mutate(ba_ha = (ba * 10000)/(pi*100)) %>% 
  group_by(site) %>% 
  dplyr::select(ba_ha, std, srd, site) %>% 
  dplyr::summarise(ba_mean = mean(ba_ha), 
                   ba_sd = sd(ba_ha),
                   stand_density_mean = mean(std), 
                   stand_density_sd = sd(std), 
                   srd_mean = mean(srd),
                   srd_sd = sd(srd)) %>% 
  as.data.frame()
